Hydra Battles and Cie

### 2021-07-29 doc/chapter-primrec.tex

\chapter{Primitive recursive functions}

@@

In particular, the library \href{../theories/html/hydras.MoreAck.AckNotPR.html}{MoreAck.AckNotPR} contains the well-known  proof that the Ackermann function is not primitive recursive (see Section~\vref{sect:ack-not-PR}).
MoreOver, the library \href{../theories/html/hydras.Hydra.Hydra_Theorems.html}{Hydra.Hydra\_Theorems} contains 
a proof that the length of an hydra battle (according to the initial replication factor) is not primitive recursive in general.

>>>>

\chapter{Primitive recursive functions}
\label{chapter:primrec}

@@

In particular, the library \href{../theories/html/hydras.MoreAck.html}{MoreAck.AckNotPR} contains the well-known  proof that the Ackermann function is not primitive recursive (see Section~\vref{sect:ack-not-PR}).
Moreover, the library \href{../theories/html/hydras.Hydra_Theorems.html}{Hydra.Hydra\_Theorems} contains 
a proof that the length of an hydra battle (according to the initial replication factor) is not primitive recursive in general.

### 2021-07-29 doc/part-hydras.tex

\label{sec:orgheadline91}

@@

\begin{Coqsrc}
Scheme Hydra_rect2 := Induction for Hydra Sort Type
with Hydrae_rect2 := Induction for Hydrae Sort Type.
\end{Coqsrc}

\begin{Coqsrc}
Check Hydra_rect2.
\end{Coqsrc}

\begin{Coqanswer}
Hydra_rect2
 : forall (P : Hydra -> Type) (P0 : Hydrae -> Type),
   (forall h : Hydrae, P0 h -> P (node h)) ->
    P0 hnil ->
    (forall h : Hydra, P h -> 
             forall h0 : Hydrae, P0 h0 -> P0 (hcons h h0)) ->
    forall h : Hydra, P h
\end{Coqanswer}

@@

\begin{Coqsrc}
(** All elements of s satisfy P *)

Fixpoint h_forall (P: Hydra -> Prop) (s: Hydrae) :=
  match s with
      hnil => True
    | hcons h s' => P h /\ h_forall P s'
  end.
 \end{Coqsrc}

 \begin{Coqsrc}
Lemma height_lt_size (h:Hydra) :
 height h < hsize h.
Proof.
  induction h using Hydra_rect2  with 
  (P0 :=  h_forall (fun h =>  height h < hsize h)).
 \end{Coqsrc}

>>>>

\label{sec:orgheadline91}
\label{chapter:hydras}

@@

\input{movies/snippets/Hydra_Definitions/HydraRect2}

\input{movies/snippets/Hydra_Examples/HydraRect2Check}

@@

\input{movies/snippets/Hydra_Definitions/hForall}

\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Examples.html}{Hydra.Hydra\_Examples}}

\input{movies/snippets/Hydra_Examples/heightLtSizea}
